ML Estimation of Matrix t Distributions with Expectation Maximization

### 2016-12-11 paper.tex
Fix header
Now compiles

\author{Zahari Kassabov\thanks{TIF-UNIMI-2016-5}\\
        Dipartimento di Fisica, Universit\`a di Torino and INFN, Sezione di Torino\\
		TIF Lab, Dipartimento di Fisica, Universit\`a di Milano\\
        E-mail: \email{kassabov@to.infn.it}\\
        \\
        Hsien-Ching Kao\\
        Wolfram Research, Inc.\\
		Champaign, Illinois 61820, USA\\
		E-mail: \email{sp000088@gmail.com}
		}

>>>>

\author{Zahari Kassabov\thanks{TIF-UNIMI-2016-5}\\
        Dipartimento di Fisica, Universit\`a di Torino and INFN, Sezione di Torino\\
		TIF Lab, Dipartimento di Fisica, Universit\`a di Milano\\
        \texttt{kassabov@to.infn.it}\\
        \and
        Hsien-Ching Kao\\
        Wolfram Research, Inc.\\
		Champaign, Illinois 61820, USA\\
		\texttt{sp000088@gmail.com}
		}
